\documentclass[11pt,a4paper]{article}

% ==========================================================================
% Alessandro Spina --- Curriculum Vitae
% Source: cv.tex
% Compile: pdflatex cv.tex   (run twice for correct page-count in header)
% Output: cv.pdf  -->  copy/rename into ../files/Alessandro_CV_<date>.pdf
% ==========================================================================

\usepackage[a4paper,margin=1in,top=0.9in,bottom=1in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{lastpage}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}

% ----- Date stamp shown in the page header (update on each revision) -----
\newcommand{\cvdate}{May 2026}

% ----- Section format: bold + horizontal rule below ----------------------
\setcounter{secnumdepth}{0}
\titleformat{\section}[hang]{\Large\bfseries}{}{0em}{}[\vspace{2pt}\titlerule]
\titlespacing{\section}{0pt}{1.4em}{0.6em}

% ----- Page header (suppressed on page 1) --------------------------------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Alessandro Spina --- Curriculum Vitae}
\fancyhead[R]{\cvdate\ --- \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

\fancypagestyle{firstpage}{%
  \fancyhf{}\renewcommand{\headrulewidth}{0pt}%
}

% ----- CV entry: bold institution / italic right-aligned date / detail ---
\newcommand{\cventry}[3]{%
  \noindent\textbf{#1}\hfill\textit{#2}\par
  #3\par\medskip
}

% ----- List layout -------------------------------------------------------
\setlist[enumerate]{leftmargin=*, itemsep=4pt, topsep=2pt}

\begin{document}
\thispagestyle{firstpage}

% =========================================================================
\begin{center}
{\Huge\bfseries Alessandro Spina}
\end{center}

\vspace{0.6em}

% Contact block: 2 columns, equal width
\noindent
\begin{tabularx}{\textwidth}{@{}X X@{}}
Department of Finance               & \href{https://www.alessandro-spina.com/}{https://www.alessandro-spina.com/} \\
UTS Business School                  & \href{mailto:alessandro.spina@uts.edu.au}{alessandro.spina@uts.edu.au} \\
University of Technology Sydney      & \\
Ultimo NSW 2007, Australia           & \\
\end{tabularx}

% =========================================================================
\section{Education}

\cventry{University of Technology Sydney}{2024 -- present}{Assistant Professor / Lecturer in Finance}

\cventry{Copenhagen Business School}{2018 -- 2024}{Center for Financial Frictions (FRIC)\\PhD in Financial Economics}

\cventry{University of Sydney}{2022 Nov -- Dec}{Visiting Scholar}

\cventry{Copenhagen Business School}{2016 -- 2018}{Masters Advanced Economics and Finance, OECON}

\cventry{University of Sydney}{2006 -- 2008}{BA Econometrics and Finance}

% =========================================================================
\section{Research Interests}

Empirical macro-finance, Financial Intermediation, Monetary Policy

% =========================================================================
\section{Research Papers}

\begin{enumerate}
\item \textbf{Corporate Loan Spreads and Economic Activity} (2025) (with Anthony Saunders, Sascha Steffen, and Daniel Streitz). \textit{Review of Financial Studies}. \href{https://academic.oup.com/rfs/article/38/2/507/7918340?guestAccessKey=478e97d8-0d2f-481e-bb53-7669945bba3a}{[Published version]} \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3717358}{[SSRN]}

\textbf{Abstract}: We investigate the predictive power of loan spreads for forecasting business cycles, specifically focusing on more constrained, intermediary-reliant firms. We introduce a novel loan-market-based credit spread constructed using secondary corporate-loan-market prices over the 1999 to 2023 period. Loan spreads significantly enhance the prediction of macroeconomic outcomes, outperforming other credit-spread indicators. The paper also explores the underlying mechanisms, differentiating between borrower fundamentals and financial frictions, with evidence suggesting that supply-side frictions are a decisive factor in loan-spread forecasting ability.

\textbf{Presentations}: NZFM Conference (2022), Danmark Nationalbank, AFA (2022), Central Bank of Ireland Workshop (2021), 11th ifo Conference on Macroeconomics and Survey Data (2021), ABFER 8th Annual Conference (2021), SFS Cavalcade (2021), FIRS (2021), Frankfurt School Finance and Management: Regulating Financial Markets Conference (2019).

\item \textbf{Disagreement in Perceptions of Monetary Policy} (sole author).

\textbf{Abstract}: Professional forecasts of U.S. monetary policy display persistent and large cross-sectional dispersion. What drives this disagreement? I distinguish between two sources: (i) heterogeneity in macroeconomic outlooks and (ii) heterogeneity in perceived monetary-policy rules. Using monthly Blue Chip Financial Forecasts (BCFF) panels, I estimate forecaster- and time-specific perceived policy rules. I construct a new disagreement measure that isolates cross-sectional dispersion in perceived policy coefficients. I find disagreement is time-varying and systematic---it rises during shifts in policy frameworks. Using a counterfactual that holds macro outlooks fixed across forecasters, I show that a sizable fraction of funds-rate forecast dispersion reflects disagreement about the policy rule, not just about the economy. Finally, I document that higher policy-rule disagreement amplifies asset-price sensitivity to FOMC announcements.

\item \textbf{Hedging Flows Around Events}, with Julian Terstegge and Paul Whelan.

\textbf{Abstract}: Asset returns around scheduled economic events, such as FOMC announcements, are commonly attributed to information revelation or risk premia. We show that part of these returns reflects predictable hedging flows by derivative dealers. Using CBOE trade data for S\&P 500 options, we construct dealer vanna, the sensitivity of dealers' aggregate option-inventory delta to changes in implied volatility. Dealer vanna is negative on average, implying that dealers must buy stocks into FOMC announcements in order to remain (delta) hedged. Exploiting time-series variation, we show that a one-standard-deviation decrease in prior-day dealer vanna predicts a 25 basis-point higher FOMC announcement-day return. Consistent with our proposed channel from expected volatility changes to derivative dealer hedging flows, we find that dealer vanna predicts signed E-mini futures volume on FOMC days. Our findings show that even narrow event windows contain systematic price pressure from intermediary rebalancing, which can distort the interpretation of event study research.
\end{enumerate}

% =========================================================================
\section{Service}

\begin{enumerate}
\item Reviewer, Journal of Banking and Finance \hfill 2021
\item Reviewer, Journal of Banking and Finance \hfill 2020
\item Discussant, NZFM Conference \hfill 2022
\item Discussant, AFBC Conference \hfill 2022
\item PhD Representative on PhD School Board \hfill 2020--2023
\item PhD Representative at Finance Department Forum \hfill 2020--2023
\item PhD Brown Bag Coordinator \hfill 2021--2023
\item Advised Masters' Theses \hfill 2020
\end{enumerate}

% =========================================================================
\section{Teaching}

\cventry{Corporate Finance (BA)}{2023--2024}{Lecturer}
\cventry{Corporate Finance (BA)}{2020--2022}{Teaching assistant to Ulf Nielsson}
\cventry{Corporate Finance (BA)}{2022}{Teaching assistant to Rama Seth}
\cventry{Macroeconomics (BA)}{2018--2019}{Teaching assistant to Anna Morin}
\cventry{Microeconomics (BA)}{2017--2019}{Teaching assistant to Martin Lau}

% =========================================================================
\section{Industry Experience}

\cventry{Jigsaw Strategic Research, Australia}{2015}{Market Research Consultant}
\cventry{Macquarie Bank, Australia}{2009 -- 2014}{Market Research Analyst}
\cventry{Ernst\&Young, Australia}{2008}{Audit Internship}

% =========================================================================
\section{References}

\noindent
\begin{tabularx}{\textwidth}{@{}X X@{}}
\textbf{David Lando} & \textbf{Daniel Streitz} \\
Professor of Finance, Center Leader of FRIC & Professor of Economics / Senior Research Advisor \\
Copenhagen Business School & University of Jena / IWH Halle \\
Solbjerg Plads 3 & Carl-Zeiß-Straße 3 \\
DK-2000 Frederiksberg & 07743 Jena \\
Denmark & Germany \\
\href{mailto:dl.fi@cbs.dk}{dl.fi@cbs.dk} & \href{mailto:daniel.streitz@uni-jena.de}{daniel.streitz@uni-jena.de} \\
\end{tabularx}

\end{document}
